Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-23 WholePlotTrajectories.tex
Update WholePlotTrajectories.tex

To counter taxonomic uncertainties due to the variability of botanical
identification levels (in space) and protocols (in time) (see {[}\#protocols{]}), the taxonomic
composition and diversity analysis were conducted at the genus level,
\emph{i.e.} referring to the genus of observed or trialed botanical
names. Trajectories of communities taxonomic and functional variations
in composition after disturbance were followed in a two-dimensional
ordination space the 30 years monitored. Two NMDS were conducted to map
either taxonomic flora inventories or communities functional composition
based on the 7 leaf, stem and life history traits (without seed mass
classes). In both cases the NMDS were performed using occurrence-based
(Jaccard) and abundance-based (Bray-Curtis) dissimilarity measures.
Trajectories along time in the plan were reported through the euclidean
distance of successive inventories to the reference inventories in 1989,
5 years after disturbance, when the uncertainty degree did not exceed
30\% of undetermined trees. The trajectories of the leaf and stem and
life traits were also visualized with the community weighted means
(CWM), representing the average trait value in a community weighted by
relative abundance of the species carrying each value
\citep{Diaz2007, Garnier2004}. To compensate the intrinsinc difference
among plots the trajectories corresponded to the differences along time
with the reference inventory in 1989. Species seed mass corresponded to
5 classes of increasing mass, seed mass trajectories were therefore
reported as the proportion of each class in the inventories.

The taxonomic diversity was assessed through Richness and the Hill
number translation of Shannon and Simpson indices \citep{Hill1973}.
These three indices belong to the set of HCDT or generalized entropy,
respectively corresponding to the 0, 1 and 2 order of diversity (q),
recomended for diversity studies \citep{Patil1982, Tothmeresz1995}. The
functional diversity was reported using the Rao index of quadratic
entropy which combines species abundance distribution and average
pairwise dissimilarity based on all functional and life traits.

@@

The functional redundancy was measured as the overlap among species in
communities' functional space \citep{Carmona2016}. The samples of the
trait database were first mapped in a 2-dimensional plan from a PCA
analysis. Then, multivariate kernel density estimator associated with
individual trees returned species traits probability distribution (TDP).
Species TDP weighted by species abundance were eventually summed for
each community: the functional redundancy was the sum of TDPs overlap,
expressed as the average number of species that could be removed from
without reducing the functional space (see appendix I for a more
comprehensive sheme).

>>>>

To counter taxonomic uncertainties due to the variability of botanical
identification levels (in space) and protocols (in time) (see {[}\#protocols{]}), the taxonomic
composition and diversity analysis were conducted at the genus level,
\emph{i.e.} referring to the genus of observed or trialed botanical
names. Trajectories of communities taxonomic and functional variations
in composition after disturbance were followed in a two-dimensional
NMDS ordination space the 30 years monitored. In both cases the NMDS were performed using occurrence-based
(Jaccard) and abundance-based (Bray-Curtis) dissimilarity measures.
Trajectories along time in the plan were reported through the euclidean
distance of successive inventories to the reference inventories in 1989,
i.e. 2-3 years after disturbance, when the uncertainty degree did not exceed
30\% of undetermined trees. To compensate the intrinsinc difference
of initial position among plots, the trajectories corresponded to the euclidian differences along time
with the reference position in 1989. Univariate trajectories of the leaf, stem and
life-history traits were inspected with the community weighted means
(CWM)
\citep{Diaz2007, Garnier2004}. Species seed mass corresponded to
5 classes of increasing mass, seed mass trajectories were therefore
reported as the proportion of each class in the inventories.

The taxonomic diversity was assessed through Richness and the Hill
number translation of Shannon and Simpson indices \citep{Hill1973}.
These three indices belong to the set of HCDT or generalized entropy,
respectively corresponding to the 0, 1 and 2 order of diversity (q),
recomended for diversity studies \citep{Patil1982, Tothmeresz1995, Marcon2015}. The
functional diversity was reported using the Rao index of quadratic
entropy which combines species abundance distribution and average
pairwise dissimilarity based on all functional and life traits.

@@

The functional redundancy was measured as the overlap among species in
community functional space \citep{Carmona2016}. The samples of the
trait database were first mapped in a 2-dimensional plan from a PCA
analysis. Then, multivariate kernel density estimator associated with
individual trees returned species traits probability distribution (TDP).
Species TDP weighted by species abundance were eventually summed for
each community: the functional redundancy was the sum of TDPs overlap,
expressed as the average number of species that could be removed from
without reducing the functional space (see appendix I for a more
comprehensive sheme).
